---
title: "The colorRamp2 package"
author: "Zuguang Gu (z.gu@dkfz.de)"
date: '`r Sys.Date()`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The colorRamp2 package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


The `colorRamp2()` function can generate a color mapping function from a vector of break values
and a vector of corresponding colors. Other colors are linearly interpolated in a certain color space.


```{r, fig.width = 6}
library(colorRamp2)

col_fun = colorRamp2(c(0, 0.5, 1), c("blue", "white", "red"))
col_fun(seq(0, 1, length = 20))


plot(NULL, xlim = c(0, 1), ylim = c(0, 1))
x = seq(0, 1, length = 20)
y = rep(0.5, 20)
points(x, y, pch = 16, col = col_fun(x), cex = 2)
```

With the color mapping function `col_fun`, colors can be mapped back to the original numeric values. Note
since colors are discrete, the values that are mapped back are not exactly identical to their original values.

```{r}
x1 = runif(10)
col = col_fun(x1)
x2 = col2value(col, col_fun = col_fun)
x1
x2
```


```{r}
sessionInfo()
```
